Introductory Physics Labs: A Tale of Two Transformations

### 2020-09-04 manuscript/onlineLabPaper.tex
Minor changes to mask self references.

Labs are supervised by Author 2, but sections are run by Graduate GTAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.

\section{Transformation \#1: Argument Driven Inquiry}
Argument Driven Inquiry (ADI) is a pedagogical method developed to make science labs
in school better match what transpires in authentic research settings
\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
answer questions, or measure quantities, that are well-known using procedures that have been
refined over time.  In ADI labs, we give students a guiding question to answer experimentally
(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''). This allows
students to design a procedure for an experiment that will answer that question, collect and
analyze their data, and make claims based on their data.  We accomplish this by having students
engage in a three-part cycle:
\begin{itemize}
  \item Pre-Lab - Introducing the context
  \item Proposal Development and Data Collection
  \item Argumentation and Peer Review
\end{itemize}
In the sections below, we will comment on each part of the cycle, focusing on both students and
GTAs. Each lab course completes at least three cycles (usually four in the Fall and Spring),
and the semester ends with a practical exam where students engage in this process on a
shortened cycle without peer feedback.\cite{Wolf2019} We have provided supplemental materials
with more details about each of the labs in our curriculum.

>>>>

Labs are supervised by Author 2, but sections are run by Graduate GTAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.

\section{Transformation \#1: Argument Driven Inquiry}
Argument Driven Inquiry (ADI) is a pedagogical method developed to make science labs
in school better match what transpires in authentic research settings
\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
answer questions, or measure quantities, that are well-known using procedures that have been
refined over time.  In ADI labs, we give students a guiding question to answer experimentally
(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''). This allows
students to design a procedure for an experiment that will answer that question, collect and
analyze their data, and make claims based on their data.  We accomplish this by having students
engage in a three-part cycle:
\begin{itemize}
  \item Pre-Lab - Introducing the context
  \item Proposal Development and Data Collection
  \item Argumentation and Peer Review
\end{itemize}
In the sections below, we will comment on each part of the cycle, focusing on both students and
GTAs. Each lab course completes at least three cycles (usually four in the Fall and Spring),
and the semester ends with a practical exam where students engage in this process on a
shortened cycle without peer feedback.\cite{Wolf2019mask} We have provided supplemental materials
with more details about each of the labs in our curriculum.
